Democracy, Public Support, and Measurement Uncertainty

### 2021-05-04 paper/dcpo_demsupport.Rmd
uncertaint claasseen

```{r claassenAJPS, eval=TRUE}
# Pooled model -----
# regime = ifelse(sd2$Regime_VD > 1, 1, 0)

ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

tidy_result_cls <- map(df_result_cls, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

@@

glance_result_cls <- map(df_result_cls, function(aResult){
  if(class(aResult) == "plm"){ 
    glance.plm(aResult) # using the customized glance function
  }else{
      glance(aResult)
    }
})

names(tidy_result_cls) <- names(glance_result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

save(tidy_result_cls, glance_result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDA"))
```

@@

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
    )
)

tidy_result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

  summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))
})

save(tidy_result_clsUncertain, file = "estimates_clsAJPS.RDS")
```

```{r dcpoPointAJPS}
# Not showing in the final result
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country"))
}) %>% 
  group_by(country, year) %>% 
  summarise(theta = mean(theta), 
            sigma = mean(sigma))

save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))

@@

ls_mod <- paste0(
  "Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + ", 
  c("plm::lag(theta, 1)", 
    "plm::lag(theta_dem, 1) + plm::lag(theta_aut, 1) "), 
  " + plm::lag(lg_imp_mdpgdp, 1) +
             plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) +
             plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)"
)

df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result),
           n = nobs(result))
})

save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

@@

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('Country', 'Year'))"
    )
)

tidy_result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

  summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))
})

save(tidy_result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```

@@

load(here::here("output", "estimates_clsMeanAJPS.RDA"))
load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

df_plot <- df_result_cls[[1]] %>% 
  mutate(model = "Claassen 2020a")

df_plot <- df_result_clsUncertain[[1]] %>% 
  mutate(model = "Claassen w/ Uncertainty") %>%  
  bind_rows(df_plot)

df_plot <- df_result_dcpoAJPS[[1]] %>% 
  mutate(model = "DCPO") %>%  
  bind_rows(df_plot)

>>>>

```{r claassenAJPS, eval=TRUE}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

tidy_cls <- map(df_result_cls, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

@@

glance_cls <- map(df_result_cls, function(aResult){
  if(class(aResult) == "plm"){ 
    glance.plm(aResult) # using the customized glance function
  }else{
      glance(aResult)
    }
})

result_cls <- map2(tidy_cls, glance_cls, ~ list(.x, .y))
names(result_cls) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

save(result_cls, file = here::here("output", "estimates_clsMeanAJPS.RDS"))
```

@@

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
    )
)

result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  if(class(result[[1]]) == "plm"){ 
    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
  }else{
    glance_clsUncertain <- glance(result[[1]])
  }

  result_clsUncertain <- list(tidy_clsUncertain, glance_clsUncertain)
})

names(result_clsUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

save(result_clsUncertain, file = "estimates_clsAJPS.RDS")
```

```{r dcpoPointAJPS, eval = TRUE}
# ls_country <- levels(dcpo_input$data$kk)
# first_year <- min(dcpo_input$data$year)
# 
# df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
#   dcpo_theta$theta[anEntry,,] %>% 
#     reformat_dcpo_output("theta") %>% 
#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
#               by = c("year", "country"))
# }) %>% 
#   group_by(country, year) %>% 
#   summarise(theta = mean(theta), 
#             sigma = mean(sigma))
# 
# save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))

@@

ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = df_dcpoMeanAJPS)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = df_dcpoMeanAJPS, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)

df_result_dcpo <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

tidy_dcpo <- map(df_result_cls, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

glance_dcpo <- map(df_result_cls, function(aResult){
  if(class(aResult) == "plm"){ 
    glance.plm(aResult) # using the customized glance function
  }else{
      glance(aResult)
    }
})

result_dcpo <- map2(tidy_dcpo, glance_dcpo, ~ list(.x, .y))
names(result_dcpo) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

save(result_dcpo, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

@@

ls_mod <- c(
    glue("plm({ls_eq}, model = 'pooling', data = aData)"),
    glue(
        "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
    )
)

result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  if(class(result[[1]]) == "plm"){ 
    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
  }else{
    glance_dcpoUncertain <- glance(result[[1]])
  }

  result_dcpoUncertain <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
})

names(result_dcpoUncertain) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

save(result_dcpoUncertain, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```

@@

load(here::here("output", "estimates_clsMeanAJPS.RDS"))
load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
)
